### 2021-04-21 paper/ase21/checker.tex
Revised Sec. 3
Revised Sec. 4

\begin{table}
  \centering
  \caption{Type-related specification bugs fixed by pull requests for the recent
  three years from 2018 to 2021.}
  \label{table:pr-bugs}
  \vspace*{-1.5em}
  \[
    \begin{array}{c|l|r|r}
      \multicolumn{1}{c|}{\textbf{Category}} &
      \multicolumn{1}{c|}{\textbf{Bug Kind}} &
      \multicolumn{1}{c|}{\textbf{\# PR}} &
      \multicolumn{1}{c}{\textbf{\# Bugs}}\\
      \hline

      \multirow{2}{*}{\stextsf{Reference}}
      & \stextsf{UnknownVar} & 5 & 12\\\cline{2-4}
      & \stextsf{DuplicatedVar} & 2 & 12\\\hline

      \multirow{1}{*}{\stextsf{Arity}}
      & \stextsf{MissParam} & 2 & 4\\\hline

      \multirow{1}{*}{\stextsf{Assertion}}
      & \stextsf{Assertion} & 4 & 5\\\hline

      \multirow{2}{*}{\stextsf{Operand}}
      & \stextsf{NoNumber} & 1 & 2\\\cline{2-4}
      & \stextsf{Abrupt} & 5 & 6\\\hline

@@

We develop a \textit{bug detector} to statically detect type-related
specification bugs in ECMAScript using an augmented abstract transfer
$\detector$ with additional checkers.  Before implementing checkers, we manually
investigated pull requests for the recent three years from 2018 to 2021 to get
insight of checkers.  As described in Table~\ref{table:pr-bugs}, there existed
19 pull requests that fixed 41 type-related specification bugs classified in
four categories and six kinds.  To detect such specification bugs, we implement
four checkers for four bug categories: a \textit{reference checker}, an
\textit{arity checker}, an \textit{assertion checker}, and an \textit{operand
checker}.  Now, we explain how each checker detects corresponding category of
bugs in the augmented abstract transfer $\detector$.

@@

In ECMAScript abstract algorithms, variables are dynamically introduced in any
contexts.  A \textit{reference bug} occurs when trying to access not yet defined
variables (\stextsf{UnknownVar}) or to redefine already defined variables
(\stextsf{DuplicatedVar}).  According to our manual investigation of pull
requests, the reference bug is the most prevalent type-related specification
bugs; 5 pull requests fixed 12 unknown variable bugs and 2 pull requests fixed
12 already defined variable bugs.  We implement the reference checker by adding
additional checks to abstract semantics of variable lookups and variable
declarations:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{\columnwidth}{!}{$
    \begin{array}{@{}l@{~}c@{~}l@{}}
      \aseme{\x}(\aenv) &=& \left\{
        \begin{array}{ll}
          \text{unknown variable} \; $\x$
          & \text{if} \; \asemr{\x}(\aenv) = \{ \tabsent \}\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\

      \asemi{\kwlet \; \x = \expr}(\lab, \tys)(\aelem) &=& \left\{
        \begin{array}{ll}
          \text{already defined variable} \; $\x$
          & \text{if} \; \aty = \{ \true \}\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\ &&
      \text{where} \; \aty = \aseme{\x \kwexists}(\aelem(\lab, \tys))\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
If the abstract semantics of a variable lookup for $\x$ is a singleton $\{
\tabsent \}$, $\x$ is always an unknown variable.  For example, consider the
syntax-directed algorithm at the upper-left in Figure~\ref{fig:example}.  Since
the \textbf{GetReferencedName} algorithm is removed, the variable
\code{GetReferencedName} does not exist in abstract environments and its lookup
returns $\{ \tabsent \}$ thus the reference checker reports the unknown variable
bug for \code{GetReferencedName}.  For already defined variables, the reference
checker utilizes the abstract semantics of existence check $\aseme{\x
\kwexists}$ to check whether the variable $\x$ of each variable declaration is
already defined.

@@

Arity of a function $\func = \kwdef \; \f (\p_1, \cdots, \p_n, \kwsl \cdots, p_m
\kwsr). \; \lab$ is defined as an interval $[n, m]$ where $n$ and $m-n$ denote
numbers of normal and optional parameters, respectively.  In function
invocations, \textit{missing parameters} (\stextsf{MissParam}) bugs occurs when
the number of arguments is not matched with the function arity.  In three years,
2 pull requests fixed 4 missing parameter bugs.  The arity checker detects such
missing parameters by using additional checks in the abstract semantics of
function call instructions:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{\columnwidth}{!}{$
    \begin{array}{@{}l@{}}
      \asemi{\x = \kwrl \expr \; \expr_1 \cdots \expr_k \kwrr}(\lab,
      \tys)(\aelem) =\\
      \qquad \left\{
        \begin{array}{ll}
          \text{missing parameters} \; \p_{k+1}, \cdots, \p_{n_\func} &
          \text{if} \; \exists \func \in \aty. \;\text{s.t.}\; k < n_\func\\

          \cdots &
          \text{otherwise}\\
        \end{array}
      \right.\\
      \qquad \text{where} \; \func = \kwdef \; \f (\p_1, \cdots, \p_{n_\func},
      \kwsl \cdots, p_{m_\func} \kwsr). \; \lab \;\wedge\;\\
      \qquad \phantom{\text{where}} \; \aty = \aseme{\expr}(\aelem(\lab,
      \tys)).\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
For each function $\func$ in the abstract semantics of the function expression
$\expr$, the arity checker compares the number of arguments with the arity of
$\func$ to detect missing parameters.  For example, consider the lower-left
syntax directed algorithm in Figure~\ref{fig:example}.  The algorithm invocation
in line 2 is compiled to a function call instruction:
\[
  \fcode{x = (formal.IteratorBindingInitialization formal)}
\]
with a temporal variable $\x$.  While it passes only a single argument
$\code{formal}$, the function arity is $[3, 3]$ thus the arity checker reports
missing parameter bugs for two additional parameters $\code{iteratorRecord}$ and
$\code{environment}$.

\subsection{Assertion Checker}
An \textit{assertion failure} (\stextsf{Assertion}) is a specification bug that
occurs when the condition of an assertion instruction is not true.  There
existed 4 pull requests that fixed 5 assertion failures.  The assertion checker
detects such bugs using additional checks in the abstract semantics of assertion
instructions:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{0.95\columnwidth}{!}{$
    \begin{array}{@{}l@{~}l@{}}
      \asemi{\kwassert \; \expr}(\lab, \tys)(\aelem) = & \left\{
        \begin{array}{ll}
          \text{assertion failure} \; \expr &
          \text{if} \; \{ \true \} \norder \aty\\

          \cdots &
          \text{otherwise}\\
        \end{array}
      \right.\\ &
      \text{where} \; \aty = \aseme{\expr}(\aelem(\lab, \tys))\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
It checks whether $\{ \true \}$ does not have partial order with the abstract
semantics of the condition expression $\expr$.  For example, consider the
lower-right syntax directed algorithm in Figure~\ref{fig:example}.  The
parameter $\code{environment}$ of this algorithm has an environment record or
$\undefval$.  Since type sensitivity divides the abstract types of arguments to
upcasted single types, there are two different abstract environments whose
variable $\code{environment}$ points to $\{ \code{Environment} \}$ or $\{
\undefval \}$.  When $\code{environment}$ is $\{ \code{Environment} \}$, the
abstract semantics of assertion condition $\code{environment = originalEnv}$ is
$\{ \tbool \}$.  Even though we know that the type of $\code{originalEnv}$ is
also $\{ \code{Environment} \}$, \code{Environment} is not a singleton type thus
we cannot convince that they are the exactly same environment.  Thus, we cannot
say that the assertion must be failed in this case.  However, if
$\code{environment}$ is $\{ \undefval \}$, the abstract semantics of the
condition $\code{environment = originalEnv}$ is $\{ \false \}$ because an
environment is never equal to $\undefval$.  Thus, the assertion checker reports
an assertion failure for the condition $\code{environment = originalEnv}$.

@@

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/func}
    \caption{The number of functions.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/view}
    \caption{The number of views.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/iter}
    \caption{The number of iterations.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/time}
    \caption{The analysis time.}
  \end{subfigure}
  \caption{The statistics of type analysis using $\tool$ for 864 versions of
  ECMAScript.}
  \vspace*{-1.5em}
  \label{fig:stat}
\end{figure*}

Several operators are typed and a \textit{ill-typed operand bug} occurs when
the type of an operand is not conform to the expected type.  For example, the
comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.
If an expression tries to compare between non-numeric values such as $\true <
\code{"abc"}$, then it is a non-numeric operand bug (\stextsf{NoNumber}).
Besides, ECMAScript has a special implicit conversion for normal completions
when their actual values stored in the $\code{Value}$ field are required
including conditions, values of field updates, operands of operators, etc.  For
example, if the variable $\x$ has a normal completion with \code{42} as its
actual value, $\code{x + 1}$ should \code{43} because the normal completion
implicitly converted into its actual value \code{42}.  To explicitly represent
this conversion, let's define a unary operator $\escaped$:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{\columnwidth}{!}{$
    \escaped \val = \left\{
      \begin{array}{ll}
        \val &
        \text{if} \; \val \; \text{is not a completion}\\

@@

        \text{unchecked abrupt completion} \; \val &
        \text{otherwise}\\
      \end{array}
    \right.
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
and assume that the operator $\escaped$ is used when the actual value is
required.  Then, an unchecked abrupt completion bug (\stextsf{Abrupt}) occurs
when the actual value is required but it is an abrupt completion.  According to
our manual investigation, 1 pull request is related to 2 non-numeric operand
bugs and 5 pull requests are related to 6 unchecked abrupt completion bugs.

The operand checker detects such ill-typed operand bugs by using additional
checks in the abstract semantics of binary operations and unary operations:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{0.9\columnwidth}{!}{$
    \begin{array}{@{}l@{~}c@{~}l@{}}
      \aseme{\expr_0 \bop \expr_1}(\aenv) &=& \left\{
        \begin{array}{ll}
          \text{ill-typed operand} \; \expr_0
          & \text{if} \; \asemr{\expr_0}(\aenv) \norder \aty_0\\
          \text{ill-typed operand} \; \expr_1
          & \text{if} \; \asemr{\expr_1}(\aenv) \norder \aty_1\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\

      \aseme{\uop \; \expr}(\aenv) &=& \left\{
        \begin{array}{ll}
          \text{ill-typed operand} \; $\expr$
          & \text{if} \; \asemr{\expr}(\aenv) \norder \aty\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
where $\aty_0$, $\aty_1$, and $\aty$ are expected abstract types of $\expr_0$,
$\expr_1$, and $\expr$, respectively.  The additional check reports when the
given operand does not conform to the expected types.  For example, consider the
upper-right built-in algorithm $\code{Math.round}$ in Figure~\ref{fig:example}.
The parameter $\x$ has $\{ \tjs \}$ and $\n$ has $\{ \tnum \}$ because the
\textbf{ToNumber} algorithm always return number values or abrupt completions
but later cases are removed by the \textbf{ReturnIfAbrupt} prefix ?.  While the
built-in algorithm correctly uses $\n$ in line 2, it misuses $\x$ in line 3 and
4 and $\{ \tjs \}$ does not have a partial order with the expected abstract type
$\{ \tnum, \tbigint \}$.  Thus, the operand type checker reports non-numeric
operand bugs.

>>>>

\begin{table}
  \centering
  \caption{Type-related specification bugs fixed by pull requests for the recent
  three years from 2018 to 2021}
  \label{table:pr-bugs}
  \vspace*{-1em}
  \[
\renewcommand{\arraystretch}{1.2}
    \begin{array}{c|l|r|r}
      \multicolumn{1}{c|}{\textbf{Category}} &
      \multicolumn{1}{c|}{\textbf{Bug Kind}} &
      \multicolumn{1}{c|}{\textbf{\# Pull Requests}} &
      \multicolumn{1}{c}{\textbf{\# Bug Fixes}}\\
      \hline \hline

      \multirow{2}{*}{\stextsf{\footnotesize Reference}}
      & \stextsf{\footnotesize UnknownVar} & 5 & 12\\\cline{2-4}
      & \stextsf{\footnotesize DuplicatedVar} & 2 & 12\\\hline

      \multirow{1}{*}{\stextsf{\footnotesize Arity}}
      & \stextsf{\footnotesize MissingParam} & 2 & 4\\\hline

      \multirow{1}{*}{\stextsf{\footnotesize Assertion}}
      & \stextsf{\footnotesize Assertion} & 4 & 5\\\hline

      \multirow{2}{*}{\stextsf{\footnotesize Operand}}
      & \stextsf{\footnotesize NoNumber} & 1 & 2\\\cline{2-4}
      & \stextsf{\footnotesize Abrupt} & 5 & 6\\\hline \hline

@@

We develop a \textit{bug detector} to statically detect type-related
specification bugs in ECMAScript using an augmented abstract transfer
$\detector$ with additional checkers.  Before implementing checkers, we manually
investigated pull requests for the recent three years from 2018 to 2021 to identify
important bugs to detect.  As summarized in Table~\ref{table:pr-bugs},
we found 19 pull requests that fixed 41 type-related specification bugs,
and classified the bugs into four categories with six kinds.
To detect them automatically, we implement four checkers:
a \textit{reference checker}, an \textit{arity checker},
an \textit{assertion checker}, and an \textit{operand checker}.

@@

ECMAScript abstract algorithms dynamically introduce variables in any contexts.
A \textit{reference bug} occurs when trying to access variables not yet defined (\stextsf{UnknownVar})
or to redefine variables already defined (\stextsf{DuplicatedVar}).
According to our manual investigation of the pull requests,
the reference bug is the most prevalent type-related specification bugs;
five pull requests fixed 12 unknown variable bugs and two pull requests fixed
12 duplicated variable declaration bugs.  We implement a reference checker by adding
additional checks to the abstract semantics of variable lookups and variable
declarations as follows:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{\columnwidth}{!}{$
    \begin{array}{@{}l@{~}c@{~}l@{}}
      \aseme{\x}(\aenv) &=& \left\{
        \begin{array}{ll}
          \text{unknown variable} \; $\x$
          & \text{if} \; \asemr{\x}(\aenv) = \{ \tabsent \}\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\

      \asemi{\kwlet \; \x = \expr}(\lab, \tys)(\aelem) &=& \left\{
        \begin{array}{ll}
          \text{already defined variable} \; $\x$
          & \text{if} \; \aty = \{ \true \}\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\ &&
      \text{where} \; \aty = \aseme{\x \kwexists}(\aelem(\lab, \tys))\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
If the abstract semantics of a variable lookup for $\x$ is a singleton $\{ \tabsent \}$,
$\x$ is always an unknown variable.  For example, consider the syntax-directed algorithm
at the upper-left part in Figure~\ref{fig:example}.
Since the \textbf{GetReferencedName} algorithm is removed, the variable
\code{GetReferencedName} does not exist in abstract environments and its lookup
returns $\{ \tabsent \}$. Thus, the reference checker reports the unknown variable
bug for \code{GetReferencedName}.  For duplicated variable declarations,
the reference checker utilizes the abstract semantics of the existence check
$\aseme{\x \kwexists}$ to see whether the variable $\x$ of each variable declaration is
already defined.

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/func}
    \caption{The number of functions}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/view}
    \caption{The number of views}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/iter}
    \caption{The number of iterations}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/time}
    \caption{The analysis time}
  \end{subfigure}
  \caption{The statistics of type analysis using $\tool$ for 864 versions of
  ECMAScript}
  \vspace*{-1em}
  \label{fig:stat}
\end{figure*}

@@

The arity of a function \mbox{\small
$\func=\kwdef\ \f (\p_1, \cdots, \p_n, \kwsl \cdots, p_m \kwsr).\lab$}
is an interval $[n, m]$ where $n$ and $m-n$ denote the
numbers of normal and optional parameters, respectively.
In function invocations, an \textit{arity bug} occurs when
the number of arguments does not match with the function arity (\stextsf{MissingParam}).
In the last three years, two pull requests fixed four missing parameter bugs.
The arity checker detects them by adding an additional check to the abstract semantics of
the function call instruction:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{\columnwidth}{!}{$
    \begin{array}{@{}l@{}}
      \asemi{\x = \kwrl \expr \; \expr_1 \cdots \expr_k \kwrr}(\lab,
      \tys)(\aelem) =\\
      \qquad \left\{
        \begin{array}{ll}
          \text{missing parameters} \; \p_{k+1}, \cdots, \p_{n_\func} &
          \text{if} \; \exists \func \in \aty. \;\text{s.t.}\; k < n_\func\\

          \cdots &
          \text{otherwise}\\
        \end{array}
      \right.\\
      \qquad \text{where} \; \func = \kwdef \; \f (\p_1, \cdots, \p_{n_\func},
      \kwsl \cdots, p_{m_\func} \kwsr). \; \lab \;\wedge\;\\
      \qquad \phantom{\text{where}} \; \aty = \aseme{\expr}(\aelem(\lab,
      \tys)).\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
For each function $\func$ in the abstract semantics of the function expression
$\expr$, the arity checker compares the number of arguments with the arity of
$\func$ to detect missing parameters.  For example, consider the lower-left
syntax-directed algorithm in Figure~\ref{fig:example}.  The algorithm invocation
on line 2 is compiled to the following function call instruction:
\[
  \fcode{x = (formal.IteratorBindingInitialization formal)}
\]
using a temporary variable $\x$.  Because it passes only a single argument
$\code{formal}$ even though the function arity is $[3, 3]$, the arity checker reports
missing parameter bugs for two additional parameters $\code{iteratorRecord}$ and
$\code{environment}$.

\subsection{Assertion Checker}
An \textit{assertion failure} (\stextsf{Assertion}) is a specification bug that
occurs when the condition of an assertion instruction is not true.
We found four pull requests that fixed five assertion failures.
The assertion checker detects them using an additional check in the
abstract semantics of the assertion instruction:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{0.95\columnwidth}{!}{$
    \begin{array}{@{}l@{~}l@{}}
      \asemi{\kwassert \; \expr}(\lab, \tys)(\aelem) = & \left\{
        \begin{array}{ll}
          \text{assertion failure} \; \expr &
          \text{if} \; \{ \true \} \norder \aty\\

          \cdots &
          \text{otherwise}\\
        \end{array}
      \right.\\ &
      \text{where} \; \aty = \aseme{\expr}(\aelem(\lab, \tys))\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
It checks whether the abstract semantics of the condition expression $\expr$ 
subsumes $\{ \true \}$.  For example, consider the lower-right syntax-directed
algorithm in Figure~\ref{fig:example}.  The parameter $\code{environment}$ of
this algorithm has an environment record or $\undefval$.
Since type sensitivity divides the abstract types of arguments to
upcasted single types, there are two different abstract environments whose
variable $\code{environment}$ points to $\{ \code{Environment} \}$ or $\{ \undefval \}$.
When $\code{environment}$ is $\{ \code{Environment} \}$, the
abstract semantics of the assertion condition $\code{environment = originalEnv}$ is $\{ \tbool \}$.
Even though we know that the type of $\code{originalEnv}$ is
also $\{ \code{Environment} \}$, because \code{Environment} is not a singleton type,
we cannot conclude that they are the exactly same environment.
Thus, the assertion checker does not report any bug for this case.
However, if $\code{environment}$ is $\{ \undefval \}$, the abstract semantics of the
condition $\code{environment = originalEnv}$ is $\{ \false \}$ because an
environment is never equal to $\undefval$.
Therefore, the assertion checker reports an assertion failure for
the condition $\code{environment = originalEnv}$.

@@

An \textit{ill-typed operand bug} occurs when
the type of an operand does not conform to its corresponding parameter type.
For example, the comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.
If an expression tries to compare non-numeric values such as $\true <
\code{"abc"}$, then it is a non-numeric operand bug (\stextsf{NoNumber}).
Besides, ECMAScript has a special implicit conversion for normal completions
when their actual values stored in the $\code{Value}$ field are necessary
such as conditions, values of field updates, and operands of operators.
For example, if the variable $\x$ has a normal completion with \code{42} as its
actual value, $\code{x + 1}$ should be \code{43} because the normal completion
gets implicitly converted into its actual value \code{42}.
To explicitly represent this conversion, we define a unary operator
$\escaped$ as follows:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{\columnwidth}{!}{$
    \escaped \val = \left\{
      \begin{array}{ll}
        \val &
        \text{if} \; \val \; \text{is not a completion}\\

@@

        \text{unchecked abrupt completion} \; \val &
        \text{otherwise}\\
      \end{array}
    \right.
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
and assume that the operator $\escaped$ is used when the actual value is necessary.
Then, an unchecked abrupt completion bug (\stextsf{Abrupt}) occurs
when the actual value is necessary but it is an abrupt completion.
According to our manual investigation, one pull request fixed two non-numeric operand
bugs and five pull requests fixed six unchecked abrupt completion bugs.

The operand checker detects such ill-typed operand bugs by additional
checks in the abstract semantics of operations:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{0.9\columnwidth}{!}{$
    \begin{array}{@{}l@{~}c@{~}l@{}}
      \aseme{\expr_0 \bop \expr_1}(\aenv) &=& \left\{
        \begin{array}{ll}
          \text{ill-typed operand} \; \expr_0
          & \text{if} \; \asemr{\expr_0}(\aenv) \norder \aty_0\\
          \text{ill-typed operand} \; \expr_1
          & \text{if} \; \asemr{\expr_1}(\aenv) \norder \aty_1\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\

      \aseme{\uop \; \expr}(\aenv) &=& \left\{
        \begin{array}{ll}
          \text{ill-typed operand} \; \expr\ \ \,
          & \text{if} \; \asemr{\expr}(\aenv) \norder \aty\\
          \cdots
          & \text{otherwise}\\
        \end{array}
      \right.\\
    \end{array}
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
where $\aty_0$, $\aty_1$, and $\aty$ are expected abstract types of $\expr_0$,
$\expr_1$, and $\expr$, respectively.  The additional checks report
when a given operand does not conform to its expected type.  For example, consider the
upper-right built-in algorithm $\code{Math.round}$ in Figure~\ref{fig:example}.
The types of $\x$ and $\n$ are $\{ \tjs \}$ and $\{ \tnum \}$, respectively, because the
\textbf{ToNumber} algorithm always returns number values or abrupt completions,
and the prefix ? of \textbf{ReturnIfAbrupt} removes the latter case.
The built-in algorithm misuses $\x$ rather than $\n$ on lines 3 and 4,
and because the expected abstract type $\{ \tnum, \tbigint \}$ does not subsume $\{ \tjs \}$,
the operand checker reports non-numeric operand bugs.
